Wikipedia Text Mining and Entropy Analysis

### 2018-10-23 english_unigram&ce&mi.Rmd
Created pipeline for wiki_analysis
changes

tkns <- extract_tokens("child", 6, 20, prov_utterances)

@@

mi <- map(counts, all_pairwise_mi)

@@

ggplot(mi[[4]], aes(x = pos1, y = mi, color = as.factor(pos2))) + 
  facet_wrap(~length) + 
  geom_point() + 
  geom_line()

>>>>

tkns <- new_get_tokens("child", 6, 20, prov_utterances)

@@

mi <- map(counts, all_pairwise_mi) %>% bind_rows()

@@

ggplot(mi, aes(x = pos1, y = mi, color = as.factor(pos2))) + 
  facet_wrap(~length) + 
  geom_point() + 
  geom_line()

### 2018-10-23 wiki_entropy/wiki_entropy.Rmd
touched up wiki_entropy
changes

```{r python_background}
## Here's where to find the languages of Wikipedia, and their prefixes https://en.wikipedia.org/wiki/List_of_Wikipedias#Detailed_list

LANGUAGE <- "Alemannic" ##This is the language you want to examine

@@

```{r slope_analysis, include=FALSE, eval = F}
extract_wiki_tokens <- function(min_length, max_length, utterances) {

@@

df <- read_csv("~/Documents/Labwork/Joe/Positional-Information/wiki_entropy/als_df.csv")

wiki_tokens %>%
    filter(word_order %in% c(1,2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = sum(n)) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10() #log length stats

als_slopes <- get_wiki_slopes(min_length = 6, max_length = 50, utterances=df, 100)
```

```{r slope_code, include = F, eval=F}
start_slope <- function(df) {

>>>>

```{r python_background}
# Here's where to find the languages of Wikipedia and their prefixes: https://en.wikipedia.org/wiki/List_of_Wikipedias#Detailed_list

LANGUAGE <- "Dutch" # This is the language you want to examine

@@

```{r slope_analysis, include=FALSE, eval = F}
df <- read_csv("~/Documents/Labwork/Joe/Positional-Information/wiki_entropy/ru_df.csv")

wiki_tokens %>%
    filter(word_order %in% c(1, 2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = sum(n)) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10() #log length stats

REPS <- 100

ru_slopes <- get_wiki_slopes(min_length = 6, max_length = 50, utterances=df, REPS)
```

```{r slope_code, include = F, eval=F}
extract_wiki_tokens <- function(min_length, max_length, utterances) {

@@

start_slope <- function(df) {
